Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2021-04-01 mice_synthesizing/paper.Rmd
Add text on imputation parameters.

@@

Choosing an adequate method to impute the data is of the utmost importance, as a flawed imputation model will drastically reduce the data utility in further inferences. Therefore, imputation models should be as flexible as possible, as this allows to capture most of the patterns in the data, and to model, possibly unanticipated, data characteristics [@murray_multiple_2018; @rubin_18years_1996]. Parametric methods, albeit easy to implement in practice, may be too restrictive to capture generally complex patterns in the data, especially in the case of nonlinear relations and interactions between multiple variables. Classification and regression trees [CART; @breiman_cart_1984] allow to model more complex patterns in the data, and have therefore been suggested as an appropriate imputation method [@reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014]. Loosely speaking, CART sequentially splits the predictor space into non-overlapping regions in such a way that the within-region variance is as small as possible after every split. As such, CART does not impose any parametric distribution on the data, making it a widely applicable method that allows for a large variety of relationships within the data [@islr_2013]. Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, we illustrate the performance of `mice` with CART as the specified imputation method.

>>>>

<!-- 
WHY WE NEED SYNTHETIC DATA - PARAGRAPHS FROM Lazer, D., Pentland, A. S., Adamic, L., Aral, S., Barabasi, A. L., Brewer, D., Gutmann, M. (2009). Life in the network: The coming age of computational social science. Science, 323(5915), 721. http://doi.org/10.1111/j.1083-6101.2007.00367.x

There are also enormous institutional obsta-cles to advancing a computational social sci-ence.  In  terms  of  approach,  the  subjects  ofinquiry in physics and biology present differentchallenges  to  observation  and  intervention.Quarks and cells neither mind when we dis-cover their secrets nor protest if we alter theirenvironments during the discovery process. Asfor infrastructure, the leap from social scienceto a computational social science is larger thanfrom  biology  to  a  computational  biology,largely due to the requirements of distributedmonitoring, permission seeking, and encryp-tion. There are fewer resources available in thesocial  sciences,  and  even  the  physical  (andadministrative) distance between social sciencedepartments and engineering or computer sci-ence departments tends to be greater than forthe other sciences. Perhaps the thorniest challenges exist on thedata side, with respect to access and privacy.Much of these data are proprietary (e.g., mobilephone and financial transactional information).The debacle following AOL’s public release of“anonymized” search records of many of itscustomers highlights the potential risk to indi-viduals and corporations in the sharing of per-sonal data by private companies (14). Robustmodels  of  collaboration  and  data  sharingbetween industry and academia are needed tofacilitate research and safeguard consumer pri-vacy and provide liability protection for corpo-rations. More generally, properly managing pri-vacy  issues  is  essential.  As  the  recent  U.S.National  Research  Council’s  report  on  geo-graphical information system data highlights, itis often possible to pull individual profiles outof even carefully anonymized data (15). Lastyear, the U.S. National Institutes of Health andthe Wellcome Trust abruptly removed a num-ber of genetic databases from online access(16). These databases were seemingly anony-mized,  simply  reporting  the  aggregate  fre-quency of particular genetic markers. How-ever, research revealed the potential for de-anonymization, based on the statistical powerof the sheer quantity of data collected fromeach individual in the database (17).Because a single dramatic incident involv-ing a breach of privacy could produce rulesand statutes that stifle the nascent field of com-putational  social  science,  a  self-regulatoryregime of procedures, technologies, and rulesis needed that reduces this risk but preservesresearch potential. As a cornerstone of such aself-regulatory regime, U.S. Institutional Re-view Boards (IRBs) must increase their techni-cal knowledge to understand the potential forintrusion and individual harm because newpossibilities do not fit their current paradigmsfor harm. Many IRBs would be poorly equip-ped to evaluate the possibility that complexdata could be de-anonymized. Further, it maybe necessary for IRBs to oversee the creationof  a  secure,  centralized  data  infrastructure.Currently,  existing  data  sets  are  scatteredamong many groups, with uneven skills andunderstanding  of  data  security  and  widelyvarying  protocols.  Researchers  themselvesmust develop technologies that protect privacywhile preserving data essential for research.These systems, in turn, may prove useful forindustry in managing customer privacy anddata security (18). -->

@@

Choosing an adequate method to impute the data is paramount, as a flawed imputation model will drastically reduce the data utility in further inferences. Imputation models should be as flexible as possible to capture most of the patterns in the data, and to model, possibly unanticipated, data characteristics [@murray_multiple_2018; @rubin_18years_1996]. Parametric methods, albeit easy to implement in practice, may be too restrictive to capture generally complex patterns in the data, especially in the case of nonlinear relations and interactions between multiple variables. Classification and regression trees [CART; @breiman_cart_1984] allow to model more complex patterns in the data, and have therefore been suggested as an appropriate imputation method [@reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014]. Loosely speaking, CART sequentially splits the predictor space into non-overlapping regions in such a way that the within-region variance is as small as possible after every split. As such, CART does not impose any parametric distribution on the data, making it a widely applicable method that allows for a large variety of relationships within the data [@islr_2013]. Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, we illustrate the performance of `mice` with CART as the specified imputation method.

## Synthe*miz*ing in practice

Additional parameters that come with the use of CART are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both restrain the flexibility of the imputation model. The values of these parameters ought to adhere to the call for imputation models that are as flexible as possible. Hence, the complexity parameter fixed at `cp = 1e-08` rather than the default `1e-08` and the minimum number of observations in each terminal node set at `minbucket = 3` rather than the default 5. The bias and variance of the final estimates justified these decisions. Additionally, the number of imputations was set to $m = 5$.
